Dunnett's test

### 2022-08-30 text/22/dunnetts-test.Rmd
Good first draft of analysis-of-means.Rmd
Minor fix to dunnetts-test

Dunnett's test is easy to implement. Calculate the traditional measures in analysis of variance, including mean squared error (MSE). You can skip the traditional F Test that you see in most ANOVA tables. It won't hurt your overall alpha level, as long as you only look at each treatment versus the control. Simply compare each treatment mean minus the control mean to a cutoff value using percentiles from a special table for Dunnett's test. The value of d depends on alpha (the desired Type I error rate for a two-sided test), g (the number of groups including the control group) and n (the number of data points in each group). Note that some tables define g as the number of groups excluding the control group.

>>>>

Dunnett's test is easy to implement. Calculate the traditional measures in analysis of variance, including mean squared error (MSE). You can skip the traditional F Test that you see in most ANOVA tables. It won't hurt your overall alpha level, as long as you only look at each treatment versus the control. Simply compare each treatment mean minus the control mean to a cutoff value using percentiles from a special table for Dunnett's test. The critical value for Dunnett's test depends on alpha (the desired Type I error rate for a two-sided test), g (the number of groups including the control group) and n (the number of data points in each group). Note that some tables define g as the number of groups excluding the control group.
